Accelerated oblique random survival forests

### 2022-07-14 paper/jmlr/main.tex
paper update, slide fix

For each risk prediction task, we completed 5 runs of Monte-Carlo cross validation. In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}. Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions. If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.

@@

After collecting data from 5 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 2,170 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model. Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models. Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets. The intercept, $\widehat{\gamma}_0$, was the expected value of the outcome using \texttt{aorsf-fast}, making the coefficients in $\widehat{\gamma}$ the expected differences between \texttt{aorsf-fast} and other learners. Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.

@@

Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}). Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.12 points higher, a relative increase of 9.30\%. The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.95, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.63 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})

@@

Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}). Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.612 points higher, a relative increase of 0.797\%. The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.96, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.02 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})

@@

Overall, \texttt{aorsf-negate} had the highest C-statistic in 21 out of 36 VI tasks, with an overall mean of 75.3 (Figure \ref{fig:bm_vi_viz}). Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.34 points higher, a relative increase of 3.21\%. Among each of the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables and the smallest advantage for interaction variables.

@@

\hspace{1em}aorsf-fast & 0.132 (0.114) & 0.774 (0.072) & 0.833 & 0.173\\
\hspace{1em}aorsf-cph & 0.131 (0.115) & 0.772 (0.072) & 2.477 & 0.174\\
\hspace{1em}aorsf-net & 0.130 (0.118) & 0.772 (0.072) & 131.969 & 0.176\\
\hspace{1em}rsf-standard & 0.121 (0.118) & 0.761 (0.075) & 2.070 & 0.291\\
\hspace{1em}cif-standard & 0.120 (0.101) & 0.768 (0.071) & 4.499 & 15.774\\
\hspace{1em}cif-rotate & 0.119 (0.129) & 0.758 (0.080) & 43.469 & 9.418\\
\hspace{1em}obliqueRSF-net & 0.119 (0.088) & 0.773 (0.071) & 388.086 & 24.864\\
\hspace{1em}glmnet-cox & 0.115 (0.123) & 0.761 (0.074) & 0.693 & 0.004\\
\hspace{1em}ranger-extratrees & 0.104 (0.090) & 0.763 (0.068) & 2.147 & 1.592\\
\hspace{1em}cif-extension & 0.099 (0.095) & 0.764 (0.072) & 23.953 & 8.487\\
\hspace{1em}aorsf-random & 0.095 (0.085) & 0.742 (0.065) & 2.288 & 0.174\\
\hspace{1em}xgboost-cox & 0.076 (0.105) & 0.757 (0.088) & 4.399 & 0.005\\
\hspace{1em}nn-cox & 0.045 (0.101) & 0.648 (0.137) & 16.081 & 5.931\\
\hspace{1em}xgboost-aft & -4.80 (5.11) & 0.767 (0.077) & 14.692 & 0.007\\

@@

\hspace{1em}ranger-extratrees & 0.028 (0.018) & 0.737 (0.042) & 0.053 & 0.155\\
\hspace{1em}aorsf-random & 0.024 (0.019) & 0.732 (0.042) & 0.452 & 0.036\\
\hspace{1em}cif-standard & 0.024 (0.039) & 0.741 (0.060) & 1.460 & 4.523\\
\hspace{1em}cif-extension & 0.022 (0.021) & 0.716 (0.055) & 9.093 & 4.176\\
\hspace{1em}obliqueRSF-net & 0.020 (0.030) & 0.733 (0.056) & 26.723 & 16.653\\
\hspace{1em}aorsf-cph & 0.017 (0.032) & 0.736 (0.056) & 0.452 & 0.037\\
\hspace{1em}aorsf-fast & 0.016 (0.027) & 0.733 (0.054) & 0.153 & 0.034\\
\hspace{1em}glmnet-cox & 0.011 (0.023) & 0.735 (0.034) & 0.180 & 0.002\\
\hspace{1em}aorsf-net & 0.010 (0.041) & 0.731 (0.055) & 19.025 & 0.036\\
\hspace{1em}xgboost-cox & 0.006 (0.046) & 0.747 (0.052) & 3.312 & 0.003\\
\hspace{1em}rsf-standard & 0.004 (0.042) & 0.721 (0.058) & 0.466 & 0.061\\
\hspace{1em}nn-cox & 0.001 (0.007) & 0.589 (0.138) & 10.976 & 0.666\\
\hspace{1em}cif-rotate & -0.002 (0.050) & 0.728 (0.051) & 14.852 & 4.031\\
\hspace{1em}xgboost-aft & -7.31 (0.690) & 0.739 (0.040) & 9.771 & 0.006\\

@@

\hspace{1em}cif-extension & 0.004 (0.012) & 0.794 (0.066) & 12.087 & 5.085\\
\hspace{1em}obliqueRSF-net & 0.003 (0.012) & 0.822 (0.064) & 8.856 & 11.019\\
\hspace{1em}aorsf-fast & 0.001 (0.019) & 0.830 (0.062) & 0.094 & 0.020\\
\hspace{1em}cif-standard & 0.000 (0.022) & 0.797 (0.079) & 1.505 & 4.550\\
\hspace{1em}aorsf-random & 0.000 (0.016) & 0.793 (0.090) & 0.247 & 0.023\\
\hspace{1em}aorsf-cph & -0.001 (0.018) & 0.811 (0.073) & 0.361 & 0.022\\
\hspace{1em}xgboost-cox & -0.005 (0.003) & 0.500 (0.000) & 0.116 & 0.002\\
\hspace{1em}nn-cox & -0.006 (0.003) & 0.514 (0.102) & 10.371 & 0.517\\
\hspace{1em}aorsf-net & -0.006 (0.034) & 0.813 (0.070) & 13.008 & 0.023\\
\hspace{1em}ranger-extratrees & -0.006 (0.022) & 0.768 (0.078) & 0.041 & 0.127\\
\hspace{1em}rsf-standard & -0.027 (0.060) & 0.796 (0.074) & 0.097 & 0.037\\
\hspace{1em}cif-rotate & -0.030 (0.037) & 0.727 (0.092) & 12.924 & 3.575\\
\hspace{1em}glmnet-cox & -0.057 (0.096) & 0.777 (0.062) & 0.282 & 0.003\\
\hspace{1em}xgboost-aft & -23.5 (7.27) & 0.772 (0.100) & 8.740 & 0.006\\

@@

\hspace{1em}aorsf-fast & 0.156 (0.005) & 0.806 (0.004) & 4.321 & 1.354\\
\hspace{1em}aorsf-net & 0.153 (0.004) & 0.806 (0.003) & 515.337 & 1.480\\
\hspace{1em}aorsf-cph & 0.152 (0.005) & 0.806 (0.004) & 14.632 & 1.349\\
\hspace{1em}rsf-standard & 0.149 (0.006) & 0.797 (0.003) & 7.394 & 1.041\\
\hspace{1em}obliqueRSF-net & 0.145 (0.002) & 0.808 (0.002) & 3100.286 & 413.186\\
\hspace{1em}cif-standard & 0.133 (0.002) & 0.806 (0.002) & 69.980 & 358.577\\
\hspace{1em}glmnet-cox & 0.132 (0.008) & 0.795 (0.003) & 1.467 & 0.025\\
\hspace{1em}nn-cox & 0.123 (0.008) & 0.793 (0.004) & 82.973 & 106.367\\
\hspace{1em}ranger-extratrees & 0.112 (0.001) & 0.792 (0.003) & 271.533 & 63.785\\
\hspace{1em}cif-rotate & 0.106 (0.001) & 0.782 (0.006) & 578.571 & 68.467\\
\hspace{1em}aorsf-random & 0.098 (0.004) & 0.771 (0.004) & 11.278 & 1.387\\
\hspace{1em}cif-extension & 0.070 (0.001) & 0.784 (0.004) & 163.371 & 49.091\\
\hspace{1em}xgboost-cox & 0.062 (0.016) & 0.811 (0.004) & 8.980 & 0.014\\
\hspace{1em}xgboost-aft & -4.81 (0.208) & 0.812 (0.004) & 21.435 & 0.021\\

@@

\hspace{1em}rsf-standard & 0.218 (0.004) & 0.790 (0.001) & 11.948 & 1.186\\
\hspace{1em}aorsf-net & 0.218 (0.006) & 0.792 (0.003) & 958.228 & 2.380\\
\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.003) & 22.614 & 2.249\\
\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.003) & 7.190 & 2.258\\
\hspace{1em}obliqueRSF-net & 0.208 (0.004) & 0.792 (0.003) & 7161.062 & 322.057\\
\hspace{1em}cif-standard & 0.202 (0.004) & 0.789 (0.004) & 64.173 & 379.745\\
\hspace{1em}glmnet-cox & 0.191 (0.017) & 0.777 (0.006) & 1.852 & 0.018\\
\hspace{1em}nn-cox & 0.183 (0.016) & 0.781 (0.003) & 95.577 & 77.835\\
\hspace{1em}ranger-extratrees & 0.181 (0.006) & 0.779 (0.005) & 350.659 & 58.944\\
\hspace{1em}cif-rotate & 0.152 (0.005) & 0.755 (0.006) & 577.948 & 65.954\\
\hspace{1em}xgboost-cox & 0.134 (0.015) & 0.795 (0.001) & 11.789 & 0.015\\
\hspace{1em}aorsf-random & 0.130 (0.004) & 0.733 (0.003) & 18.944 & 1.995\\
\hspace{1em}cif-extension & 0.114 (0.001) & 0.775 (0.005) & 180.959 & 50.040\\
\hspace{1em}xgboost-aft & -1.63 (0.238) & 0.795 (0.002) & 25.690 & 0.014\\

@@

\hspace{1em}aorsf-fast & 0.236 (0.005) & 0.842 (0.006) & 5.253 & 1.671\\
\hspace{1em}rsf-standard & 0.231 (0.005) & 0.835 (0.004) & 10.275 & 1.254\\
\hspace{1em}aorsf-net & 0.231 (0.004) & 0.842 (0.005) & 628.786 & 1.736\\
\hspace{1em}aorsf-cph & 0.231 (0.006) & 0.842 (0.006) & 16.545 & 1.568\\
\hspace{1em}obliqueRSF-net & 0.215 (0.003) & 0.841 (0.005) & 3701.023 & 306.739\\
\hspace{1em}cif-standard & 0.200 (0.002) & 0.839 (0.005) & 67.705 & 364.696\\
\hspace{1em}nn-cox & 0.181 (0.029) & 0.823 (0.008) & 79.949 & 112.151\\
\hspace{1em}glmnet-cox & 0.179 (0.036) & 0.821 (0.010) & 1.899 & 0.012\\
\hspace{1em}ranger-extratrees & 0.173 (0.003) & 0.825 (0.006) & 260.123 & 63.679\\
\hspace{1em}cif-rotate & 0.171 (0.003) & 0.806 (0.005) & 581.803 & 66.846\\
\hspace{1em}aorsf-random & 0.141 (0.004) & 0.792 (0.004) & 13.281 & 1.509\\
\hspace{1em}xgboost-cox & 0.119 (0.009) & 0.844 (0.005) & 13.603 & 0.015\\
\hspace{1em}cif-extension & 0.110 (0.003) & 0.809 (0.006) & 167.897 & 48.511\\
\hspace{1em}xgboost-aft & -3.93 (0.269) & 0.843 (0.005) & 22.308 & 0.022\\

@@

\hspace{1em}aorsf-fast & 0.094 (0.003) & 0.794 (0.003) & 3.786 & 1.160\\
\hspace{1em}rsf-standard & 0.092 (0.003) & 0.786 (0.005) & 5.225 & 0.875\\
\hspace{1em}aorsf-net & 0.091 (0.003) & 0.793 (0.004) & 411.476 & 1.233\\
\hspace{1em}aorsf-cph & 0.090 (0.003) & 0.792 (0.004) & 13.452 & 1.127\\
\hspace{1em}obliqueRSF-net & 0.082 (0.002) & 0.791 (0.004) & 1751.465 & 410.345\\
\hspace{1em}glmnet-cox & 0.079 (0.005) & 0.785 (0.004) & 1.493 & 0.011\\
\hspace{1em}cif-standard & 0.074 (0.002) & 0.788 (0.004) & 78.679 & 394.309\\
\hspace{1em}nn-cox & 0.072 (0.016) & 0.782 (0.008) & 28.811 & 84.991\\
\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.006) & 310.500 & 70.135\\
\hspace{1em}aorsf-random & 0.059 (0.004) & 0.752 (0.007) & 9.207 & 1.136\\
\hspace{1em}cif-rotate & 0.052 (0.002) & 0.768 (0.009) & 614.088 & 69.548\\
\hspace{1em}xgboost-cox & 0.047 (0.012) & 0.792 (0.001) & 6.854 & 0.014\\
\hspace{1em}cif-extension & 0.036 (0.001) & 0.772 (0.007) & 163.803 & 49.613\\
\hspace{1em}xgboost-aft & -6.78 (0.231) & 0.791 (0.002) & 21.692 & 0.023\\

@@

\hspace{1em}aorsf-fast & 0.099 (0.018) & 0.718 (0.013) & 0.228 & 0.047\\
\hspace{1em}cif-standard & 0.099 (0.016) & 0.712 (0.013) & 1.158 & 3.454\\
\hspace{1em}aorsf-cph & 0.097 (0.018) & 0.716 (0.012) & 0.646 & 0.051\\
\hspace{1em}aorsf-net & 0.095 (0.014) & 0.716 (0.010) & 48.543 & 0.049\\
\hspace{1em}aorsf-random & 0.095 (0.009) & 0.717 (0.012) & 1.361 & 0.045\\
\hspace{1em}cif-rotate & 0.095 (0.020) & 0.712 (0.011) & 12.821 & 3.474\\
\hspace{1em}obliqueRSF-net & 0.089 (0.005) & 0.716 (0.010) & 250.693 & 16.565\\
\hspace{1em}rsf-standard & 0.084 (0.026) & 0.705 (0.008) & 1.193 & 0.135\\
\hspace{1em}cif-extension & 0.080 (0.007) & 0.708 (0.013) & 10.097 & 4.783\\
\hspace{1em}ranger-extratrees & 0.078 (0.010) & 0.709 (0.017) & 0.494 & 0.239\\
\hspace{1em}glmnet-cox & 0.076 (0.018) & 0.703 (0.024) & 0.112 & 0.002\\
\hspace{1em}xgboost-cox & 0.060 (0.006) & 0.699 (0.010) & 2.915 & 0.003\\
\hspace{1em}nn-cox & -0.005 (0.003) & 0.521 (0.030) & 12.067 & 1.890\\
\hspace{1em}xgboost-aft & -1.06 (0.351) & 0.707 (0.013) & 13.225 & 0.006\\

@@

\hspace{1em}aorsf-fast & 0.097 (0.012) & 0.710 (0.009) & 0.227 & 0.055\\
\hspace{1em}aorsf-cph & 0.096 (0.011) & 0.709 (0.008) & 0.639 & 0.052\\
\hspace{1em}aorsf-net & 0.096 (0.016) & 0.710 (0.012) & 51.707 & 0.045\\

>>>>

For each risk prediction task, we completed 20 runs of Monte-Carlo cross validation. In each run, we used a random sample containing 50\% of the available data for training and the remaining 50\% for testing each of the learners described in \secref{sec:learners}. Then, for each learner, we computed the IPA, time-dependent C-statistic, and computational time required to fit a prediction model and compute risk predictions. If any learner failed to obtain predictions on any particular split of data\footnote{For example, when the prediction task was to predict risk of death in the ACTG 320 clinical trial (26 events total), some splits did not leave enough events in the training data to fit complex learners such as the neural network}, the results for that split were omitted from downstream analyses.

@@

After collecting data from 20 replications of Monte-Carlo cross validation for the 14 learners in all 31 risk prediction tasks, we analyzed the resulting 8,680 observations of IPA and, separately, time-dependent C-statistic, using a Bayesian linear mixed model. Our approach follows the ideas described by \citet{benavoli2017time} and \citet{tidymodels}, who developed guidelines on making statistical comparisons between learners using Bayesian models. Specifically, we fit two models: $$\text{IPA} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}) $$ and $$\text{C-stat} = \widehat{\gamma}_0 + \widehat{\gamma} \cdot \text{learner} + (1\,|\, \text{data/run}).$$ Random intercepts for specific splits of data (\ie, \texttt{run} in the model formula) were nested within datasets. The intercept, $\widehat{\gamma}_0$, was the expected value of the outcome using \texttt{aorsf-fast}, making the coefficients in $\widehat{\gamma}$ the expected differences between \texttt{aorsf-fast} and other learners. Default priors from \texttt{rstanarm} were applied for model fitting \citep{rstanarm}.

@@

Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest IPA in  out of 31 risk prediction tasks, with an overall mean IPA of  (Figure \ref{fig:bm_pred_viz_ibs}). Compared to the learner with the second highest mean IPA (\texttt{rsf-standard}), \texttt{aorsf-fast}'s mean was 1.27 points higher, a relative increase of 10.5\%. The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected IPA was 0.98, and the posterior probability of \texttt{aorsf-fast} having a superior IPA to other learners ranged from 0.76 (versus \texttt{rsf-standard}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_ibs})

@@

Compared to learners that were not oblique RSFs, \texttt{aorsf-fast} had the highest time-dependent C-statistic in  out of 31 risk prediction tasks, with an overall mean of  (Figure \ref{fig:bm_pred_viz_cstat}). Compared to the learner with the second highest mean C-statistic (\texttt{obliqueRSF-net}), \texttt{aorsf-fast}'s mean was 0.643 points higher, a relative increase of 0.837\%. The posterior probability of \texttt{aorsf-fast} and \texttt{aorsf-cph} having practically equivalent expected time-dependent C-statistics was 0.99, and the posterior probability of \texttt{aorsf-fast} having a superior time-dependent C-statistic versus other learners ranged from 0.01 (versus \texttt{obliqueRSF-net}) to $>$0.999 (versus several other learners; see Figure \ref{fig:bm_pred_model_viz_cstat})

@@

Overall, \texttt{aorsf-negate} had the highest C-statistic in 27 out of 36 VI tasks, with an overall mean of 76.1 (Figure \ref{fig:bm_vi_viz}). Compared to the VI technique with the second highest overall C-statistic (\texttt{aorsf-anova}), \texttt{aorsf-negate}'s mean was 2.22 points higher, a relative increase of 3.00\%. Among the four relevant variable classes, \texttt{aorsf-negate} had the highest mean C-statistic for main effects, combination effects, and non-linear effects, with the greatest advantage of using \texttt{aorsf-negate} occurring among non-linear and combination variables.

The three techniques that used `aorsf` to estimate VI were ranked first (negation), second (ANOVA), and third (permutation) in overall mean C-statistic across all of the simulation scenarios. Computationally, ANOVA VI was the fastest technique with a median average

@@

\hspace{1em}aorsf-fast & 0.134 (0.112) & 0.774 (0.071) & 0.772 & 0.188\\
\hspace{1em}aorsf-cph & 0.133 (0.112) & 0.773 (0.070) & 1.993 & 0.184\\
\hspace{1em}aorsf-net & 0.126 (0.127) & 0.770 (0.074) & 128.379 & 0.177\\
\hspace{1em}rsf-standard & 0.121 (0.116) & 0.760 (0.075) & 2.168 & 0.291\\
\hspace{1em}cif-standard & 0.120 (0.100) & 0.768 (0.070) & 4.511 & 15.781\\
\hspace{1em}cif-rotate & 0.120 (0.128) & 0.758 (0.080) & 42.206 & 9.111\\
\hspace{1em}obliqueRSF-net & 0.120 (0.086) & 0.773 (0.071) & 376.676 & 24.742\\
\hspace{1em}glmnet-cox & 0.117 (0.122) & 0.761 (0.075) & 0.460 & 0.004\\
\hspace{1em}ranger-extratrees & 0.105 (0.088) & 0.764 (0.067) & 2.416 & 1.775\\
\hspace{1em}cif-extension & 0.100 (0.095) & 0.763 (0.072) & 23.171 & 8.367\\
\hspace{1em}aorsf-random & 0.095 (0.083) & 0.743 (0.064) & 2.272 & 0.180\\
\hspace{1em}xgboost-cox & 0.072 (0.102) & 0.757 (0.088) & 4.368 & 0.004\\
\hspace{1em}nn-cox & 0.049 (0.109) & 0.653 (0.136) & 16.163 & 4.563\\
\hspace{1em}xgboost-aft & -4.74 (5.18) & 0.767 (0.074) & 14.635 & 0.007\\

@@

\hspace{1em}aorsf-random & 0.031 (0.020) & 0.744 (0.035) & 0.408 & 0.036\\
\hspace{1em}ranger-extratrees & 0.029 (0.017) & 0.739 (0.037) & 0.052 & 0.145\\
\hspace{1em}cif-standard & 0.028 (0.027) & 0.746 (0.039) & 1.052 & 4.532\\
\hspace{1em}obliqueRSF-net & 0.028 (0.022) & 0.743 (0.039) & 26.784 & 15.942\\
\hspace{1em}aorsf-fast & 0.026 (0.027) & 0.741 (0.041) & 0.143 & 0.034\\
\hspace{1em}aorsf-cph & 0.026 (0.029) & 0.747 (0.040) & 0.433 & 0.035\\
\hspace{1em}cif-extension & 0.024 (0.015) & 0.722 (0.040) & 9.266 & 4.180\\
\hspace{1em}aorsf-net & 0.020 (0.034) & 0.742 (0.040) & 18.859 & 0.036\\
\hspace{1em}glmnet-cox & 0.018 (0.027) & 0.744 (0.035) & 0.172 & 0.002\\
\hspace{1em}rsf-standard & 0.011 (0.034) & 0.732 (0.042) & 0.145 & 0.059\\
\hspace{1em}cif-rotate & 0.008 (0.037) & 0.736 (0.035) & 15.338 & 3.967\\
\hspace{1em}nn-cox & -0.001 (0.017) & 0.638 (0.114) & 10.944 & 0.541\\
\hspace{1em}xgboost-cox & -0.002 (0.048) & 0.748 (0.033) & 3.788 & 0.003\\
\hspace{1em}xgboost-aft & -8.09 (1.44) & 0.736 (0.035) & 9.657 & 0.006\\

@@

\hspace{1em}aorsf-fast & 0.008 (0.019) & 0.835 (0.056) & 0.087 & 0.020\\
\hspace{1em}obliqueRSF-net & 0.008 (0.011) & 0.829 (0.053) & 8.678 & 10.534\\
\hspace{1em}aorsf-cph & 0.008 (0.018) & 0.827 (0.063) & 0.351 & 0.020\\
\hspace{1em}aorsf-random & 0.006 (0.014) & 0.802 (0.071) & 0.224 & 0.023\\
\hspace{1em}cif-extension & 0.001 (0.021) & 0.770 (0.069) & 8.850 & 3.780\\
\hspace{1em}ranger-extratrees & 0.000 (0.019) & 0.778 (0.073) & 0.041 & 0.126\\
\hspace{1em}aorsf-net & -0.002 (0.032) & 0.814 (0.069) & 14.142 & 0.023\\
\hspace{1em}cif-standard & -0.004 (0.025) & 0.784 (0.065) & 1.106 & 4.570\\
\hspace{1em}xgboost-cox & -0.004 (0.004) & 0.500 (0.000) & 0.111 & 0.002\\
\hspace{1em}nn-cox & -0.005 (0.004) & 0.522 (0.099) & 9.961 & 0.534\\
\hspace{1em}rsf-standard & -0.028 (0.050) & 0.780 (0.078) & 0.093 & 0.037\\
\hspace{1em}cif-rotate & -0.036 (0.048) & 0.709 (0.091) & 13.345 & 3.439\\
\hspace{1em}glmnet-cox & -0.060 (0.102) & 0.749 (0.106) & 0.275 & 0.002\\
\hspace{1em}xgboost-aft & -25.1 (7.60) & 0.778 (0.074) & 9.772 & 0.006\\

@@

\hspace{1em}aorsf-fast & 0.157 (0.007) & 0.811 (0.007) & 4.591 & 1.355\\
\hspace{1em}aorsf-cph & 0.153 (0.007) & 0.810 (0.007) & 14.698 & 1.385\\
\hspace{1em}aorsf-net & 0.153 (0.007) & 0.811 (0.007) & 507.224 & 1.477\\
\hspace{1em}rsf-standard & 0.151 (0.007) & 0.802 (0.007) & 9.099 & 1.101\\
\hspace{1em}obliqueRSF-net & 0.144 (0.005) & 0.813 (0.007) & 2836.384 & 351.006\\
\hspace{1em}cif-standard & 0.133 (0.005) & 0.810 (0.007) & 70.288 & 358.500\\
\hspace{1em}glmnet-cox & 0.129 (0.012) & 0.796 (0.008) & 1.721 & 0.011\\
\hspace{1em}nn-cox & 0.124 (0.014) & 0.796 (0.007) & 55.992 & 105.741\\
\hspace{1em}ranger-extratrees & 0.112 (0.005) & 0.796 (0.008) & 320.882 & 71.239\\
\hspace{1em}cif-rotate & 0.104 (0.004) & 0.784 (0.008) & 569.756 & 70.690\\
\hspace{1em}aorsf-random & 0.098 (0.005) & 0.773 (0.008) & 11.738 & 1.361\\
\hspace{1em}cif-extension & 0.069 (0.002) & 0.787 (0.009) & 164.896 & 51.659\\
\hspace{1em}xgboost-cox & 0.066 (0.018) & 0.815 (0.006) & 8.635 & 0.015\\
\hspace{1em}xgboost-aft & -4.92 (0.295) & 0.815 (0.005) & 22.322 & 0.013\\

@@

\hspace{1em}aorsf-net & 0.217 (0.006) & 0.792 (0.004) & 952.688 & 2.390\\
\hspace{1em}rsf-standard & 0.216 (0.007) & 0.789 (0.004) & 13.694 & 1.330\\
\hspace{1em}aorsf-fast & 0.215 (0.007) & 0.792 (0.004) & 7.760 & 2.287\\
\hspace{1em}aorsf-cph & 0.215 (0.007) & 0.791 (0.004) & 23.194 & 2.305\\
\hspace{1em}obliqueRSF-net & 0.207 (0.005) & 0.791 (0.004) & 7578.159 & 316.772\\
\hspace{1em}cif-standard & 0.201 (0.005) & 0.790 (0.004) & 72.192 & 385.603\\
\hspace{1em}nn-cox & 0.192 (0.013) & 0.780 (0.005) & 102.206 & 101.400\\
\hspace{1em}glmnet-cox & 0.189 (0.015) & 0.776 (0.007) & 2.123 & 0.012\\
\hspace{1em}ranger-extratrees & 0.181 (0.005) & 0.781 (0.005) & 421.367 & 67.011\\
\hspace{1em}cif-rotate & 0.152 (0.007) & 0.757 (0.006) & 582.264 & 65.718\\
\hspace{1em}xgboost-cox & 0.132 (0.011) & 0.794 (0.004) & 12.326 & 0.016\\
\hspace{1em}aorsf-random & 0.130 (0.005) & 0.733 (0.006) & 22.918 & 2.061\\
\hspace{1em}cif-extension & 0.112 (0.002) & 0.776 (0.005) & 182.973 & 54.549\\
\hspace{1em}xgboost-aft & -1.59 (0.150) & 0.794 (0.004) & 28.205 & 0.015\\

@@

\hspace{1em}aorsf-fast & 0.234 (0.007) & 0.842 (0.005) & 5.447 & 1.627\\
\hspace{1em}rsf-standard & 0.230 (0.007) & 0.836 (0.005) & 10.044 & 1.063\\
\hspace{1em}aorsf-cph & 0.230 (0.006) & 0.841 (0.005) & 16.965 & 1.635\\
\hspace{1em}aorsf-net & 0.216 (0.059) & 0.832 (0.045) & 632.139 & 1.707\\
\hspace{1em}obliqueRSF-net & 0.213 (0.005) & 0.842 (0.005) & 3706.701 & 311.291\\
\hspace{1em}cif-standard & 0.200 (0.004) & 0.839 (0.005) & 74.710 & 369.280\\
\hspace{1em}nn-cox & 0.188 (0.020) & 0.827 (0.009) & 66.425 & 104.654\\
\hspace{1em}cif-rotate & 0.172 (0.006) & 0.807 (0.007) & 577.084 & 67.496\\
\hspace{1em}ranger-extratrees & 0.171 (0.004) & 0.825 (0.005) & 326.124 & 84.602\\
\hspace{1em}glmnet-cox & 0.168 (0.042) & 0.818 (0.016) & 2.513 & 0.012\\
\hspace{1em}aorsf-random & 0.139 (0.005) & 0.789 (0.006) & 15.868 & 1.587\\
\hspace{1em}xgboost-cox & 0.122 (0.017) & 0.846 (0.005) & 11.223 & 0.015\\
\hspace{1em}cif-extension & 0.108 (0.003) & 0.809 (0.007) & 169.585 & 49.274\\
\hspace{1em}xgboost-aft & -3.80 (0.250) & 0.845 (0.005) & 26.160 & 0.014\\

@@

\hspace{1em}aorsf-fast & 0.094 (0.004) & 0.795 (0.007) & 4.109 & 1.124\\
\hspace{1em}rsf-standard & 0.091 (0.005) & 0.785 (0.007) & 7.142 & 0.915\\
\hspace{1em}aorsf-cph & 0.090 (0.004) & 0.793 (0.008) & 13.304 & 1.124\\
\hspace{1em}aorsf-net & 0.087 (0.018) & 0.786 (0.032) & 391.565 & 1.201\\
\hspace{1em}obliqueRSF-net & 0.082 (0.003) & 0.792 (0.007) & 1773.436 & 379.126\\
\hspace{1em}glmnet-cox & 0.078 (0.005) & 0.788 (0.007) & 1.789 & 0.010\\
\hspace{1em}cif-standard & 0.074 (0.003) & 0.789 (0.007) & 72.507 & 366.228\\
\hspace{1em}nn-cox & 0.072 (0.013) & 0.781 (0.010) & 32.716 & 93.157\\
\hspace{1em}ranger-extratrees & 0.068 (0.003) & 0.780 (0.009) & 256.826 & 67.732\\
\hspace{1em}aorsf-random & 0.059 (0.004) & 0.751 (0.009) & 9.314 & 1.118\\
\hspace{1em}cif-rotate & 0.052 (0.003) & 0.769 (0.009) & 588.245 & 70.061\\
\hspace{1em}xgboost-cox & 0.046 (0.014) & 0.794 (0.006) & 6.688 & 0.014\\
\hspace{1em}cif-extension & 0.036 (0.002) & 0.772 (0.008) & 169.525 & 51.117\\
\hspace{1em}xgboost-aft & -6.54 (0.420) & 0.793 (0.007) & 21.053 & 0.013\\

@@

\hspace{1em}aorsf-fast & 0.098 (0.014) & 0.716 (0.012) & 0.228 & 0.050\\
\hspace{1em}aorsf-cph & 0.098 (0.014) & 0.715 (0.011) & 0.632 & 0.051\\
\hspace{1em}cif-standard & 0.096 (0.014) & 0.709 (0.012) & 0.666 & 3.606\\
\hspace{1em}aorsf-random & 0.094 (0.009) & 0.714 (0.011) & 1.002 & 0.045\\
\hspace{1em}aorsf-net & 0.090 (0.025) & 0.708 (0.037) & 49.445 & 0.046\\
\hspace{1em}obliqueRSF-net & 0.088 (0.006) & 0.716 (0.012) & 250.492 & 16.952\\
\hspace{1em}cif-rotate & 0.085 (0.018) & 0.704 (0.014) & 12.226 & 3.491\\
\hspace{1em}rsf-standard & 0.084 (0.019) & 0.702 (0.010) & 1.526 & 0.149\\
\hspace{1em}ranger-extratrees & 0.082 (0.007) & 0.710 (0.011) & 0.090 & 0.245\\
\hspace{1em}cif-extension & 0.080 (0.006) & 0.708 (0.012) & 8.368 & 4.020\\
\hspace{1em}glmnet-cox & 0.073 (0.014) & 0.709 (0.017) & 0.104 & 0.003\\
\hspace{1em}xgboost-cox & 0.061 (0.013) & 0.699 (0.012) & 3.172 & 0.003\\
\hspace{1em}nn-cox & -0.003 (0.003) & 0.511 (0.022) & 11.966 & 1.368\\
\hspace{1em}xgboost-aft & -1.12 (0.214) & 0.705 (0.014) & 11.661 & 0.006\\

@@

\hspace{1em}aorsf-fast & 0.097 (0.016) & 0.711 (0.015) & 0.228 & 0.050\\
\hspace{1em}aorsf-cph & 0.096 (0.017) & 0.710 (0.014) & 0.641 & 0.050\\
\hspace{1em}cif-standard & 0.089 (0.016) & 0.698 (0.015) & 0.661 & 3.398\\
\hspace{1em}obliqueRSF-net & 0.086 (0.009) & 0.708 (0.014) & 258.163 & 16.636\\
